---
title: "R Notebook"
output: html_notebook
---

# Getting Started with R Lab

# 1_Learning_Objectives

Be able to demonstrate all the concepts from the pre-course
Be able to demonstrate best practice coding
Be able to demonstrate competent use of the RStudio IDE
Duration - 4 hours

Answer these questions in notebook

Remember to make a project.
Remember to use your best coding practices

General Package Installs:

```{r "Installing Packages 1"}
install.packages("styler")
install.packages("plyr")
library(styler)
```



# 2_Vectors

#2.1_Making_Vectors


Source for Data is a Google search of 



```{r "Weather Vectors"}
weather_temp               <- c(13, 16, 17, 16, 14)
weather_chance_of_rain     <- c(0.5, 0.2, 0.8, 0.4, 0.6)
weather_cloud_cover        <- c("Mostly Cloudy", "Showers", "Showers", "Showers", "Partly Cloudy")
weather_cloud_cover_factor <- as.factor(c("Mostly Cloudy", "Showers", "Showers", "Showers", "Partly Cloudy"))
```

Kept names with weather pretext, put percentage values of precipitation into decimal (nominal) objects and made a factor for my cloud cover vector. 

Answers:

```{r}
weather_temp
weather_chance_of_rain
weather_cloud_cover
weather_cloud_cover_factor
```


#2.2_Naming_Vectors

```{r "Naming Vectors}
days_of_week <- c("Wednesday", "Thursday", "Friday", "Saturday", "Sunday")

names(weather_temp)               <- days_of_week
names(weather_chance_of_rain)     <- days_of_week
names(weather_cloud_cover)        <- days_of_week
names(weather_cloud_cover_factor) <- days_of_week
```

Slack me for any questions on this step. 

Answers:
```{r}
weather_temp
weather_chance_of_rain
weather_cloud_cover
weather_cloud_cover_factor
```



#2.3_Means

```{r "Means"}
mean_temp <- mean(weather_temp)
mean_chance_of_rain <- mean(weather_chance_of_rain)
```

I kept both vectors as decimal values in 2.1 so calculations such as the mean do not provide any errors. 

Answers: 

```{r}
mean_temp
mean_chance_of_rain
```



# 2.4_Selecting_Vectors

```{r "Selecting Vectors"}

weather_temp[weather_temp>mean_temp]
weather_temp[weather_chance_of_rain <= mean_chance_of_rain]
weather_cloud_cover[-3:-1]

```

Bad way of selecting for the cloud cover, could check out notes for smarter options. 


# 2.5_Putting_It_Together

Answers 1-6:

```{r "Spelling Test"}
library(plyr)
test_results <- c(6, 7, 9, 7, 9, 3, 9, 7, 3, 8, 10, 5, 5, 9, 7, 5, 9, 8, 9, 5)
num_test_marks <- sum(test_results)
average_test_mark <- mean(test_results)
highest_test_mark <- max(test_results)
lowest_test_mark <- min(test_results)
frequency_of_test_marks <- c(count(test_results)["freq"])
percentage_of_test_marks <- paste((100*test_results)/10, "%")
strong_test_marks <- sum(test_results>=8)

```


```{r}
num_test_marks
average_test_mark
highest_test_mark
lowest_test_mark
frequency_of_test_marks
percentage_of_test_marks
percentage_of_test_marks <- paste((100*test_results)/10, "%")
strong_test_marks

```


# Part 3

#3.1_Creating_a_Matrix


```{r}
matrix(list(wk1_temp, wk2_temp))
```


```{r}
wk1_temp <- (weather_temp)
wk2_temp <- c(16, 15, 16, 17, 17)
ten_day_forecast_matrix <- matrix(list(wk1_temp, wk2_temp), nrow == 2, ncol == 5, dimnames = list("Week_1", "Week_2")) 

```














# Part 4

# Factors

```{r}
weather_cloud_cover_factor
days_of_week_factor <- ordered(days_of_week)
days_of_week_factor
weather_temp[days_of_week_factor>"Saturday"]
```

levels = ordered days of week, you need an extra



# Part 5


#5.1_Creating_data_frames

```{r "Data Frames"}
five_day_forecast_data <- data.frame("Temperature (°)" = weather_temp, "Chance_of_Rain (%)" = weather_chance_of_rain, "Cloud_Cover" = weather_cloud_cover, "Day_of_Week" = days_of_week_factor)
five_day_forecast_data
```


Here lies the to-be-written rm chunk to kill all my poor beautiful vector babies. 


```{r}

```
















# Part 6

#6.1_Creating_Lists

```{r}

```














# Part 7

#7.1_Harder_Questions

```{r}
number_of_sides <- 1000
triangle_number <- (number_of_sides*(number_of_sides+1))/2
triangle_number
```


```{r}

```









