---
title: "Week 3 - Day 3 homework - Jack Ogilvie-Richards"
output: html_notebook
---

# MVP - Libraries & Raw Data

Here I will load in the tidyverse library to provide tools for our data, as well as the CodeClan tweet data provided. 

```{r Library}
library(tidyverse)
```

```{r Reading .csv}
cctweets <- read_csv("data/code_clan_tweets.csv")
```

I will load the info csv file later. 

# MVP - Questions


Question 1

Find the number of rows, columns, and list all the variable names.

```{r Question 1}

dim(cctweets)

colnames(cctweets)

head(cctweets)

cctweets

```

Question 2

Summarise the number of likes (favorite_count) CodeClan tweets have. Create a boxplot to check for outliers.

```{r Question 2}

# as I was unsure if there was a grouping to which the tweet data would fall into, I've included a line of code making a new variable
# it is quite possible that as I'm grouping by id that it makes absolutely no difference but there you go. I follow with a summary, which I then apply to a boxplot. See further conclusions below:

cctweets_grouped <- group_by(cctweets, tweet_id, favorite_count)

cctweets %>%
  summarise(tweet_id, favorite_count)

ggplot(cctweets_grouped) +
  aes(x = tweet_id, y = favorite_count, group = "tweet_id") +
  geom_boxplot() +
  coord_flip()

```

Sadly, CodeClan's twitter is stuck with a grounding mean/median of 0 likes - hence while there are a large number of outliers it is fair to argue that only do the highest two values almost double the scale of the plot, a good indication of an outlier. 


Question 3

Find the total number of favourited tweets (stored in favorite_count) that CodeClan tweets have got. Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).

```{r Question 3}

# I'll be using a simple pipe to find this value, simply using the count function, specifying the two conditions by which I wish to organise the CodeClan tweets.

cctweets %>%
  count(screen_name, favorite_count > 0, is_quote == FALSE)


```

For a tweet to be added it must have at least one like, and it doesn't count if it is a quote (is_quote = TRUE). Therefore only the bottom row of my output contains all suitable tweets, of which 89 received some likes. 


Question 4

Summarise the mean number of retweets (retweet_count), split by the type of platform that was used to tweet (source). Again, omit quoted tweets from the mean.

```{r Question 4}

cctweets %>%
  group_by(source) %>%
  filter(retweet_count > 0, is_quote == FALSE) %>%
  summarise(round(mean(retweet_count), 3))

```

Using the filter function is the obvious thing to do now, hopefully someone appreciates the rounding. 


Question 5

Count the total number of likes (i.e. total of favorite_count), split by media type, and arrange them from most likes to least. Assume that any tweets without a listed media type are of type “text”.


```{r}

cctweets %>%
  mutate_if(media_type, length(media_type) == 0, "text") %>%
  summarise(media_type, sum(favorite_count>0))

```


Question 6

Find the mean number of characters that a CodeClan tweet contains.

```{r}

cctweets %>%
  mutate(media_type = replace_na(media_type, "text")) %>%
  summarise(media_type, n(favorite_count))
  



```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```































