---
title: "R Notebook"
output: html_notebook
---


```{r}
library(tidyverse)
```


```{r}


proj_management <- read.csv("data/project_management.csv")


```


```{r}

proj_management %>%
  ggplot() +
  aes(x = estimated_length, y = actual_length, label = 1:nrow(proj_management)) +
  geom_point() +
  geom_text()



```
There is a number of possible outliers (24, 18, tops of the groups at (x = 13, 16, 18)) - the obvious one in this case is '5', which is way above the general trend of values; this is an influential outlier. 



```{r}


plot(lm(actual_length ~ estimated_length, data = proj_management))


```


```{r}

plot(lm(actual_length ~ estimated_length, data = proj_management), which = 4)



```

Clearly the 5th value is outside Cook's Distance in the initial Residuals vs Leverage plot, furthermore when we observe a plot of Cook's distance values and see 5 as our main contributor. 


Now let's remove the outlier, before that though let's just see what the changes are when we remove on of the smaller outliers we identified. 

```{r}

# just to see the current intercept value
lm(proj_management$actual_length ~ proj_management$estimated_length)



```



```{r}

new_proj_management <- proj_management[-18, ]


```


```{r}

lm(new_proj_management$actual_length ~ new_proj_management$estimated_length)


```


A small change from the intercept before removing the outlier, but not an insignificant one. 

This will likely not change much about the fitting. 

```{r}

new_proj_management %>%
  ggplot() +
  aes(x = estimated_length, y = actual_length) +
  geom_point()

```


```{r}

plot(lm(new_proj_management$actual_length ~ new_proj_management$estimated_length))



```


```{r}

plot(lm(proj_management$actual_length ~ proj_management$estimated_length))


```

As you can see, there is very little change to the Residuals vs Leverage lines compared to the original regression.




Let's try with the influential outlier in row 5


```{r}


new_proj_management <- proj_management[-5, ]



```


```{r}


lm(new_proj_management$actual_length ~ new_proj_management$estimated_length)


```

A huge change in intercept value. 


```{r}

new_proj_management %>%
  ggplot() +
  aes(x = estimated_length, y = actual_length) +
  geom_point()

```


```{r}

plot(lm(new_proj_management$actual_length ~ new_proj_management$estimated_length))



```


```{r}

plot(lm(proj_management$actual_length ~ proj_management$estimated_length))


```


In the new dataset with the influential outlier omitted we can see the lines differ hugely, with the new regression keep a rather steady Reg. vs Lev.  line. 






```{r}


plot(lm(actual_length ~ estimated_length, data = proj_management))



```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```






