---
title: "Week 3 - Day 2 Homework - Jack Ogilvie-Richards"
output: html_notebook
---

# Question 1

Calling in library 'tidyverse':

```{r}
library(tidyverse)
```


Reading in CSV: 

```{r}
facial_recog <- read_csv("data/face_descriptions.csv")
```


Basic understanding of raw data - column types, initial looks, names:

```{r}

# View(facial_recog)  #if you want this to run simply remove ...
                      #... the hash at the start of the line above

dim(facial_recog)

head(facial_recog)

names(facial_recog)

```

# Question 2 

The variable names do not look tidy at all - while user_id, sex and age are relatively helpful, the t1, ... are extremely unclear. Age ideally would be integers as decimal values of a year seem inaccurate, unless I knew it was based off a date-to-numeric system - even then though it's pretty unclear and would be better to ground the ages. 

There are so many unclear columns hence our data is wide, ideally we want a lot less than 53 columns of descriptions as it's pretty overwhelming. 

Granted, this homework looks really challenging so let's just see how I go!


# Question 3

```{r}

long_facial_recog <- facial_recog %>%
  pivot_longer(-c(user_id, sex, age), 
               names_to = "test_faces", 
               values_to = "desription")

head(long_facial_recog)




```

Yay! That makes me slightly less terrified.

# Question 4

I'll be finishing the homework later, apologies.














































