---
title: "Selecting the right chart"
output: html_notebook
---

### Libraries


```{r}

library(tidyverse)
library(CodeClanData)
library(viridis)
library(forcats)

```

### Four Categories

#### 3.1 Comparison




```{r}



ggplot(late_deliveries) +
  aes(x = date, y = late_deliveries) +
  geom_line() +
  geom_smooth(alpha = 0.2) +
  labs(
    title = "Late Deliveries; 2015-2019",
    subtitle = "A comparison", 
    x = "Year",
    y = "No. of late deliveries"
  ) +
  theme_grey() 
  

```

Here we have a line chart for late delivery counts from 2015 to the end of 2018. The chart shows a gradual decrease (highlighted by the smooth curve) in late deliveries over the past 4 years, with natural oscillations at times of national holiday/celebration (Easter, Christmas, etc). An impressive change would be the improvement from 2015 to 2017 at Christmas time, where late deliveries had been reduced by a third of the total of Winter 2015. 



```{r}

recovery_times %>%
  #rename(treatment, 
  #       "control" = "Control Treatment",
   #      "treatment_a" = "Treatment Method A",
    #     "treatment_b" = "Treatment Method B") %>%
  ggplot() +
    aes(x = recovery, fill = treatment_group) +
    geom_bar(position = "dodge") +
    facet_wrap(~treatment_group, nrow = 2) +
    labs(
      title = "Patient Recovery Periods", 
      subtitle = "by Method of Treatment",
      x = "\nRecovery Time (days)",
      y = "No. of Patients"
    )
  


```


```{r}

fitness_levels %>%
  ggplot() +
  aes(x = group, y = fitness_score, fill = fitness_score > 0) +
  geom_col(position = "dodge") +
  coord_flip()


```


#### Connection


```{r}

blood_pressure %>%
  ggplot() +
  aes(x = daily_saturated_fat_intake_mg, y = systolic_blood_pressure_mm_hg) +
  geom_point()


```


```{r}

car_use %>%
  ggplot() +
  aes(x = car_use_percent, y = air_so2_concentration_ppm, size = population, colour = city) +
  geom_point()


```


#### Distribution


```{r}

d20_outcomes %>% 
  ggplot() +
  aes(x = outcome, fill = "black") +
  geom_histogram(position = "dodge") +
  labs(
    title = "D20 Class Outcomes",
    subtitle = "By university grading",
    x = "Grade",
    y = "No. of Students"
  ) +
  scale_x_continuous(breaks = c(4, 7, 11, 14, 17, 20),
                 labels = c(
                   "4" = "Fail",
                   "7" = "Pass",
                   "11" = "Good Pass",
                   "14" = "Merit",
                   "17" = "Distinction",
                   "20" = "Full Marks"
                 )) 


```


```{r}

d20x5_outcomes %>%
  ggplot() +
  aes(x = outcome) +
  geom_histogram()

```

#### Composition


```{r}

pension_surplus


```


```{r}

pension_liabilities


```

Ran a bit out of time here sorry, check homework form. 


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


