---
title: "R Notebook"
output: html_notebook
---

# Loading in libraries

```{r}
library(tidyverse)
library(CodeClanData)
```

# Reading in data

```{r}

starbucks_menu_raw <- read_csv("data/starbucks_drinkMenu_expanded.csv")

```

# Question 1 - Basic examination

```{r}

starbucks_menu_raw

```

```{r}

dim(starbucks_menu_raw)

```

```{r}

colnames(starbucks_menu_raw)

```

```{r}

names(starbucks_menu_raw)

```


# Question 2

Let’s first investigate the calories of different drinks. Select the variables Beverage_category, Beverage, Beverage prep and Calories from your data. Since we are interested in the calorie content, check if there are any NA values in the data, and drop them if there are.

```{r}

starbucks_menu_q2 <- starbucks_menu_raw %>%
  select(Beverage_category, Beverage, Beverage_prep, Calories) %>%
  filter(Calories != FALSE) # little bit unclear, explain if you have to do stuff like not equal to not...

head(starbucks_menu_q2)
```

# Question 3

Let's create a new variable (column) called calorie_diff, which stores the difference between 135 calories (135 calories = 10 cubes of sugar!) and the calories in each drink. (hint: you’ll want to subtract the calories from 135 to see which drink have more or less than 10 cups of sugar).

```{r}


starbucks_menu_q3 <- starbucks_menu_q2 %>%
  mutate(Calories, calorie_diff = 135 - Calories)
  
starbucks_menu_q3

```


# Question 4

Let's summarise the mean number of calories in each beverage_category. Which 3 drinks have the most calories? Which 3 drinks have the least? Write a small summary of your findings.


```{r}

starbucks_menu_q4_mean <- starbucks_menu_q3 %>%
  group_by(Beverage_category) %>%
  summarise(cal_mean = mean(Calories)) %>%
  arrange(desc(cal_mean))

starbucks_menu_q4_mean


```

```{r}

starbucks_menu_q4_top3 <- starbucks_menu_q3 %>%
  arrange(desc(Calories)) %>%
  head(3)

starbucks_menu_q4_top3

```

```{r}

starbucks_menu_q4_bottom3 <- starbucks_menu_q3 %>%
  arrange(desc(Calories)) %>%
  tail(3)

starbucks_menu_q4_bottom3



```

By organising the beverage_category by mean calories, we can see that Smoothies, Frappacinos & Signature Espresso drinks have the most calories in a drink on average. However, when we look at the my calorific drinks (top 3) Smoothies are nowhere to be seen. This is likely to be a result of smoothie quartiles being far closer than coffee quartiles.  It seems white chocolate adds a massive amount of calories as, even without whipped cream, the 2% milk espresso drink is the only drink with over 500 calories in it. The least calories in a drink from Starbucks comes in their basic brewed coffee options, with a single espresso containing just 5 calories, 



# Question 5


Let’s look at this a different way. What is the average number of calories in each Beverage_prep type?

```{r}

starbucks_menu_q5_mean <- starbucks_menu_q3 %>%
  group_by(Beverage_prep) %>%
  summarise(cal_mean = mean(Calories)) %>%
  arrange(desc(cal_mean))

starbucks_menu_q5_mean

```

# Question 6


Which Beverage_prep type contains more than the average calories of all drinks?
Hint: to answer this, you’ll have to first figure out what the average calories across all drinks are, and then use that as a filter for the grouped Beverage_prep data.

-- sorry about the messy chunks, I was really close to getting this and Q7 just hadn't quite cracked the ordering - I'll pay good attention to the review and swat on pipes as we use them more hopefully! --

```{r}


starbucks_menu_q6 <- starbucks_menu_q3 %>%
  select(Beverage_prep) %>%
  
  
  


starbucks_menu_q6

```

```{r}


starbucks_menu_q7 <- starbucks_menu_q5_mean %>%
  select(Beverage_prep) %>%
  summarise(cal_mean = mean(Calories)) %>%
  arrange(desc(cal_mean))

starbucks_menu_q5_mean



mean(starbucks_menu_q3$Calories) # you were on the right track, you just need to make an extra variable for this then compare
                                 # the grouped pipe mean calories with the overall mean

```

```{r}

starbucks_menu_q3 %>%
  select(Calories) %>%
  mutate(Calories, cal_mean = mean(Calories))


```



# Question 7


Which is the best type of coffee drink to get if you’re worried about consuming too many calories?



```{r}





```

```{r}

```

```{r}

```























