---
title: "Reading in data homework - Jack Ogilvie-Richards"
output: html_notebook
---

# MVP

For the MVP and the rest of the questions I'll likely need some libraries to load in my files. 

```{r}
library(readr)
library(readxl)
library()

```




#1.1 & 1.2

We need to read in our first data set, which when examined in a simple text editor reviews to be a comma separated table where the first row are the column titles. Let's see what we can do:

```{r state_income_data read}

state_income_data_raw <- read_delim(
  "data/state_income_data.csv", 
  skip = 1, 
  n_max = 20, 
  col_names = c("Index", "State", "2002", "2003", "2004", 
                "2005", "2006", "2007", "2008", "2009", 
                "2010", "2011", "2012", "2013", "2014", 
                "2015"),
  delim = ","
  )

state_income_data_raw


```

We've used a read_csv

(EDIT: actually used a read_delim function with to exactly the same fruits so works both ways I guess anyway carry on) 

function and call the data from our copied folder in our homework repository. The first row contains the titles so we want to only skip the first row; I'm taking a sample of the first 20 entries, although for a list this small it's probably okay to load the whole thing. I then specified the column names using col_names, with a bit of manual vector writing (although I'd love to see a method for making this easier by taking the Y from the front of the year and pulling the names from the first row). 


# 1.3

```{r}
cars_raw <- read_csv(
  "data/cars.csv", 
  col_types = cols(
    X1 = col_character(), 
    mpg = col_double(),
    cyl = col_double(),
    disp = col_double(),
    hp = col_double(),
    vs = col_logical()
    )
)

cars_raw
```

# 1.4 

```{r}
read_delim(
  "data/scotland.txt",
  delim = ";",
  skip = 2, 
  col_names = c("Rank", "Locality", "Population", "Status", "Council Area"),
)
```


# 1.5








# 1.6

```{r}

read_delim(
  "data/steam-200k-sample.csv", 
  delim = ",", 
  skip = 4,
  col_types = cols("bought online" = col_logical()
)
)

```



# 1.7

```{r}

read_tsv(
  "data/historic_eu_payments.tsv",
  
  )



```


#1.8

```{r}

```
































