---
title: "Week 1 - weekend homework - Jack Ogilvie-Richards"
output: html_notebook
---

# Week 1 - R Programming - weekend homework
# D4 Cohort - Jack Ogilvie-Richards
# 2 MVP

# 2.2 if statements and functions

# 2.2.1

Here we must write a function that multiplies all numbers by 15 and adds 4. 

```{r multi_add_code}
multi_add <- function(x){
  
  by_15 <- 15*x
  add_4 <- by_15 + 4
  return(add_4)

}

multi_add(1)
multi_add(2)
multi_add(3)

```

Here I have made a function which multiplies the input by 15, storing this value in a temporary value 'by_15'. I assign to a new value 'add_4' the sum of the 'by_15' value and 4.0. Once these are completed I return the 'add_4' value and close the function. 


# 2.2.2

Here we must write a function that returns “bird” if the input is “goose”, “duck” or “pigeon”, and returns “not bird” for all other input. 

Let's give it a go:

```{r is_it_a_bird code}

is_it_a_bird <- function(animal){
  bird_names <- c("goose", "duck", "pigeon")
  if(animal %in% bird_names){
    return("bird")
  }
  return("not bird")
}

is_it_a_bird("goose")
is_it_a_bird("apple")
is_it_a_bird(5)
is_it_a_bird("seagull")

```

Inside my function I made a variable containing all the birds I'm interested in, making a Boolean statement that will return TRUE if my input 'animal' is in my vector of bird names, FALSE if it isn't. With a TRUE, the function returns 'bird', with a FALSE the function moves on from the if statement and returns 'not bird'. 


# 2.2.3

In this question we need to write a function which multiplies all numbers by 10. If the input isn’t a number, the function should return “Invalid input”. 

```{r by_10_or_invalid code}

by_10_or_invalid <- function(x) {
  
  if(class(x) == "numeric"){
    x_by_10 <- 10*x
    return(x_by_10)
  }
     
  return("Invalid input")
  
}

by_10_or_invalid(2)
by_10_or_invalid(5.3)
by_10_or_invalid("x")
by_10_or_invalid(7)


```

Made a function that contained an internal if statement relying on whether the class of the input was a numeric. If so, multiply by 10 and store that in a value which is then returned. Otherwise the function simply moves onto the other return of an "Invalid input" statement. 


# 2.3.1

```{r library load 1}
library(dplyr)
```

The 'dplyr' package has been added to use some of the functions needed for the following sections. 

The first part has us looking to make a new vector which records whether a vector's elements are greater or less than or equal to 10, returning 'Big' and 'Small' respectively. 

```{r scale_of_sizes code}

sizes <- c(13, 15, 10, 8, 22)

scale_of_sizes <- ifelse(sizes[ ] > 10, "Big", "Small")

scale_of_sizes

```

Looks like it works!


# 2.3.2

Pretty simple recode() here:

```{r animals for fruit code}

fruit <- c("apple", "apple", "banana", "cherry", "cherry")

ani_fruit <- recode(fruit, "apple" = "aplaca", "banana" = "bonobo", "cherry" = "chipmunk")

ani_fruit

```


# 2.3.3

Task: 

The two vectors below show the ages at marriage of each member of a couple. The first elements of each vector correspond to the first couple, the second elements to the second couple, and so on.

Create a new vector which is equal to “Wife older” whenever the wife’s age is highest “Husband older” when the husband’s age is highest “Same age” when they are the same age. 

Solution:

```{r marriage code}

wife_age <- c(29L, 30L, 36L, 31L, 22L)
husband_age <- c(28L, 35L, 32L, 31L, 29L)

compare_age <- case_when(
  wife_age > husband_age ~ "Wife older",
  wife_age < husband_age ~ "Husband older",
  wife_age == husband_age ~ "Same age"
)

compare_age

```


# 2.4 Loops

List for following questions:

```{r required list}

my_list <- list(
  4,
  "apple",
  10.5,
  c("is", "an", "apple"),
  "apple",
  c("i", "like", "apples"),
  8
)

```

# 2.4.1

Let's take a look at the list we're using:

```{r look at list}
my_list
```

```{r print loop}

for(i in 1:length(my_list)){
  ifelse(class(my_list[[i]]) == "character", print(my_list[i]), print("not a character"))
}

```

Slightly more tricky one due to navigating the list - the method I used was recognising that while I use a for loop to go through all of the list's entries I'm still needing to change what is being returned on a condition. The 'ifelse' function is perfect for this, as with its condition checking whether each object of the list is of class 'character', if so returning the object, otherwise a negative statement. 


# 2.4.2

Task: 

Once again write a loop that prints out character elements. This time if the element has a length() greater than one, paste() all the elements in that vector together into one big character vector.

Solution: 

```{r list check pasting code}


for(i in 1:length(my_list)){
  
  if(class(my_list[[i]]) == "character"){
    
    if(length(my_list[[i]]) < 1){
      pasted_obj <- paste(my_list[[i]], collapse = " ")
      }
    
    return(pasted_obj)
    
  }
  
  return("not a character")
  
}

```

```{r}
for(i in 1:length(my_list)){
  
  ifelse(class(my_list$i) == "character" | length(my_list$i) >= 1, print(paste(my_list[i], collapse = " ")), print("not a character"))


  
  }


```


 ifelse(length(my_list[[i]]) < 1, paste(my_list[[i]], " "), my_list[i])






# Extensions

3.4


```{r}
#setting base values
x_i_minus_1 <- 0
x_i <- 1
sum_even_fib <- 0

while(x_i < 4*10^6){ # while loop that ends when our new fib number exceeds 4 million
  
  x = x_i + x_i_minus_1
  
  if(x %% 2 == 0){sum_even_fib = sum_even_fib + x}
  
  x_i_minus_1 = x_i
  
  x_i = x
  
}
  
sum_even_fib

```
















