---
title: "Time Series Modelling & Spacial Visualisation - Homework"
author: "Jack Aldred Ogilvie-Richards"
output: html_notebook
---


```{r Libraries, include=FALSE}

library(tidyverse)
library(lubridate)
library(tsibble)
library(tsibbledata)
library(fable)
library(leaflet)
library(janitor)


```

# MVP


This homework will recap basic time series, time series modelling, and spatial visualisation. 


## Question 1

```{r Loading data}


bike_data <- tsibbledata::nyc_bikes

view(bike_data)
```


```{r year, month, date columns}

bike_data <- bike_data %>%
  mutate(year_of_use = year(as_date(start_time))) %>%
  mutate(month_of_use = month(as_date(start_time))) %>%
  mutate(date_of_use = as_date(start_time))


```



## Question 2

```{r summarising hires by month}

bike_data_by_month <- bike_data %>%
  index_by(month_of_use) %>%
  summarise(hire_per_month = n())

```

```{r plotting monthly hires}

ggplot(bike_data_by_month) +
  aes(x = month_of_use, y = hire_per_month) +
  geom_line() +
  geom_smooth()

```


### Interpretation

What does this plot tell you about the time series? Do you think this downsampled data would be adequate to build a forecast with?






## Question 3

```{r}

hires_by_day <- bike_data %>%
  index_by(date_of_use) %>%
  summarise(hires_per_day = n())


```


```{r}

ggplot(hires_by_day) +
  aes(x = date_of_use, y = hires_per_day) +
  geom_line() +
  geom_smooth(alpha = .5)


```


### Interpretation

What does this plot tell you about the time series? Would this data be preferrable for time series forecasting compared to the monthly data?




## Question 4



```{r}

bike_data_explicit <- hires_by_day %>%
  fill_gaps(hires_per_day = as.integer(median(hires_per_day)))
  
  

```



```{r}
bike_model_fit <- bike_data_explicit %>%
  
  model(
    snaive_model = SNAIVE(hires_per_day),
    mean_model = MEAN(hires_per_day), 
    arima_model = ARIMA(hires_per_day)
  )

bike_model_fit

```


```{r}

bike_hire_forecast <- bike_model_fit %>%
  fabletools::forecast(h = "4 months") 
```

```{r}

bike_hire_forecast %>%
  autoplot(bike_data_explicit, level = FALSE)


```


```{r}

smaller_bike_hires <- bike_data_explicit %>%
    filter(as.integer(lubridate::year(hires_per_day)) >= 2018)



our_new_forecast %>%
  autoplot(smaller_bike_hires, level = NULL) +
  facet_wrap(~ .model, dir = "v")


```


```{r}





```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```









