---
title: "R Notebook"
output: html_notebook
---

Data Types Homework
Part 1
Question 1

```{r part_01_Q1_working}
stock_prices <- c(23, 27, 23, 21, 34, 24, 25, 30, 37, 30)
day_of_week <- rep(c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday"), times = 2)
```

Here I've created two vectors, one numerical (I have left them as decimals in case calculations would divide anything into a .5 term) and one with repeating characters (containing the days of the week). See below:

```{r part_01_Q1_soln}
stock_prices
day_of_week
```

Question 2

```{r part_01_Q2_working}
day_of_week_factor <- factor(day_of_week)
names(stock_prices) <- day_of_week
named_stock_prices <- stock_prices
```

```{r part_01_Q2_soln}
day_of_week_factor
named_stock_prices
```

Similarly here, I've set variables for the factor of each day of the week, I might not understand that I'm doing with this as I write this sentence but I'll mention if I remember what factors are as I complete the homework. Another variable was the named stock prices, which I did by setting the names of the stock price vector I made in Q1 to day_of_week, which is ordered. As we can see, this leaves named_stock_prices as a lovely named vector. 

Question 3 

```{r part_01_Q3_working+soln}
stock_data <- data.frame(day_of_week, named_stock_prices)
View(stock_data)
```

Fairly self-explanatory, set a data frame to consist of a column of days of the week and the stock prices corrosponding to that day of the week. Viewing the data frame we can see that so far, all is calm. 

Question 4

```{r part_01_Q4_working}
stock_list <- list(Stock_Value = stock_prices, Day = day_of_week, Data = stock_data)
```

```{r part_01_Q4_soln}
stock_list
```

List was made, set names to the named elements as: Stock_Value, Day, Data.


Part 2
Question 1

```{r part_02_Q1_working+soln}
stock_prices[4:6]
stock_prices[stock_prices > 30]
```

Question 2

```{r part_02_Q2_working+soln}
stock_data[ , "day_of_week"]
stock_data[stock_prices<25, ]
stock_data[ , 1]
stock_data[3, ]
stock_data[3, 1]
```

```{r part_02_Q4_working+soln}
stock_list["Data"]
```

Might look at the extension in the morning - time for bed!






