---
title: "Homework - Jack Ogilvie-Richards - Week 1/Day 3"
output: html_notebook
---

#Homework ----

Here's my homework! If you're reading this I hope it's enjoyable!

#Installing data sets: ----

```{r "Installing Data"}
install.packages('devtools')
devtools::install_github('codeclan/CodeClanData')
library(CodeClanData)
```

```{r "styler"}
install.packages("styler")
library(styler)
```

Also installed styler, promise I'll learn some of its functionality soon and hence I will install and load it each time. 


#Setting up data ----

1. Data Frame - Beer

```{r "Beer Data"}
beer_data <- data.frame(beer)
View(beer_data)
```

2. Matrix - Temp

```{r "Temperature"}
temp_matrix <- matrix(temp, nrow = 106, ncol = 12)
View(temp_matrix)
```

You may view this matrix however it is quite unreadable initially. 


3. List - game_of_thrones

```{r "Game of Thrones"}
game_of_thrones_list <- list(game_of_thrones)
View(game_of_thrones_list)
```

Thanks to the nesting of the pre-loaded list it's easy to see the various layers of nesting, with the bulk being in the nested list of characters and their gender. 

#Analysis ----

1. Beer Data

To get a quick scope of this lovely database, let's figure out the range, marker values (mean, mode) and find some dope facts! 

Looking at the View window of the beer data, you can see that ABV percentage, calories and carbohydrates are our numerical subsets, with Brand and Brewery as our non-parametric parameters (good tongue twister, that!). 

Let's finally get some numbers!

```{r Beer Analysis}
str(beer_data)
summary(beer_data)
summary(as.numeric(beer_data[ , 4]))
mean(beer_data[ , "percent"])
mean(as.numeric(beer_data[ , 4]))
max(beer_data[ , "percent"])
max(as.numeric(beer_data[ , 4]))



```

```{r "Defining Beer Data Parameters"}
min_ABV <- min(beer_data[ , "percent"])
min_calories <- min(beer_data[ , "calories"])
min_carbs <- min(beer_data[ , "carbohydrates"])
max_ABV <- max(beer_data[ , "percent"])
max_calories <- max(beer_data[ , "calories"])


```


Fact 1 - can a beer be as many calories as an average meal (400)?

```{r}

```


Fact 2 - what are the strongest beers with below average calorific content?


2. Temperatures

Let's have a look at the numbers again and see what interesting bits we can find!

```{r Temperature Analysis}
str(temp_matrix)
summary(temp_matrix)


```

Fact 1 - the year of our coldest winter (min(December))

```{r}

```


Fact 2 - Longest gap between summer temperatures being above average

Fun Fact - likelihood of getting an above average peak summer (t-test I believe??)






3. Game of Thrones


What is the fraction of female characters in Game of Thrones


```{r}
summary(game_of_thrones_list)

genders <- game_of_thrones_list["character"["gender"]]
genders
```













